\documentclass[letterpaper,10pt]{article}

% --- PACKAGES ---
\usepackage[margin=0.5in]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{charter}

% --- PAGE SETUP ---
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% --- SECTION FORMATTING ---
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% --- COMMANDS ---
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% --- DOCUMENT ---
\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \scshape BHARGAV MADHAV PRATHIVADI BHAYANKARAM} \\ \vspace{5pt}
    \small 
    \faMapMarker* \ Tempe, Arizona \ $|$ \ 
    \faPhone \ +1 (602) 696-5147 \ $|$ \ 
    \faEnvelope \ \href{mailto:Bhargavmadhav.pb@gmail.com}{Bhargavmadhav.pb@gmail.com} \ $|$ \ 
    \faLinkedin \ \href{https://linkedin.com/in/bhargav-madhav}{LinkedIn}
\end{center}

% --- PROFESSIONAL SUMMARY ---
\section{PROFESSIONAL SUMMARY}
\small

\vspace{-5pt}

% --- EXPERIENCE ---
\section{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart
\resumeSubheading{Estate Dekho}{Hyderabad, India}{Software Engineer}{Jan 2023 -- Dec 2023} \resumeItemListStart \resumeItem{Executed large-scale legacy data migration to **AWS DynamoDB** using robust **Python** data tooling, implementing advanced indexing strategies to reduce end-to-end processing latency by 60\% (from 1.5s to 600ms).}
\resumeItem{Optimized core search backend algorithms integrated within **AWS data engineering pipelines**, resulting in a significant 39\% reduction in average API response time (from 900ms to 550ms).}
\resumeItem{Developed real-time telemetry infrastructure using Python/Node.js and WebSockets, resulting in the elimination of polling overhead and enabling live state synchronization for high-traffic data streams.}
\resumeItem{Simulated comprehensive RESTful API load scenarios using Docker containerization to precisely evaluate system limits, increasing promoted listing click-through rates by 20\%.}
\resumeItem{Redesigned React/Redux frontend architecture to support dynamic content rendering, boosting user engagement metrics by over 25\%.}
 \resumeItemListEnd
\resumeSubHeadingListEnd

% --- PROJECTS ---
\section{TECHNICAL PROJECTS}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Deep Learning-based Blockchain Fraud Detection} $|$ \emph{Python, TensorFlow, Autoencoders}}{} \resumeItemListStart \resumeItem{Designed a security framework using Deep Learning to identify malicious ERC-20 smart contract transactions.}
\resumeItem{Architected the anomaly detection pipeline using Recurrent Autoencoders and TensorFlow to analyze transaction patterns in real-time.}
\resumeItem{Achieved 94\% accuracy, reduced false positives by 28\%, and prevented simulated financial losses of over \$250,000.}
 \resumeItemListEnd\resumeProjectHeading{\textbf{Loan Prediction \& Approval Pipeline} $|$ \emph{Python, Pandas, MLOps}}{} \resumeItemListStart \resumeItem{Developed an end-to-end Machine Learning solution in **Python** to automate the assessment of loan eligibility probabilities.}
\resumeItem{Built predictive models using **Scikit-learn** and automated data preprocessing workflows using **Pandas** to handle large datasets.}
\resumeItem{Reduced manual review workloads by 60\% and slashed data preparation time from 3 hours to 30 minutes, improving compliance transparency.}
 \resumeItemListEnd\resumeProjectHeading{\textbf{Crypto Payment Gateway} $|$ \emph{Blockchain, Solidity, Flask}}{} \resumeItemListStart \resumeItem{Created a decentralized payment solution enabling secure and fast micro-transactions on the blockchain.}
\resumeItem{Led a 3-engineer team to develop the backend logic using Solidity smart contracts and Flask integration.}
\resumeItem{Improved transaction speed by 45\%, cut costs by 30\%, and won 1st Prize at IEEE Hackathon for innovation.}
 \resumeItemListEnd
\resumeSubHeadingListEnd

% --- EDUCATION ---
\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading{Arizona State University}{Tempe, Arizona}{Master of Science, Information Technology}{Jan 2024 -- Dec 2025} \resumeItemListStart \resumeItem{GPA: 3.97/4.0} \resumeItem{Coursework: Advanced Big Data Analytics \& AI, NLP for IT, Visualization, Advanced DBMS, Data in Cloud} \resumeItemListEnd\resumeSubheading{Jawaharlal Nehru Technological University}{Hyderabad, India}{Bachelor of Technology, Computer Science}{Jun 2019 -- Jul 2023} \resumeItemListStart \resumeItem{GPA: 3.20/4.0} \resumeItem{Coursework: Data Structures, Data Mining, DBMS, Software Engineering, Virtual Reality} \resumeItemListEnd
\resumeSubHeadingListEnd

% --- SKILLS ---
\section{SKILLS}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, Java, C, GoLang, Solidity} \\
     \textbf{Machine Learning}{: Supervised/Unsupervised Learning, Deep Learning (CNNs, RNNs, Autoencoders), Data Science Libraries (Pandas, NumPy, Scikit-learn), NLP} \\
     \textbf{Cloud \& Infrastructure}{: AWS (DynamoDB, SageMaker, S3, Redshift, Glue), Apache Spark, Hadoop, TensorFlow, PyTorch, Docker, MLflow, Airflow, FastAPI, Git, CI/CD} \\
     \textbf{Visualization}{: Tableau, Power BI, Matplotlib, Seaborn}
    }}
\end{itemize}

% --- CERTIFICATIONS ---
\section{CERTIFICATIONS}
\resumeSubHeadingListStart
\resumeItem{AWS Data Engineering}
\resumeItem{AWS Machine Learning Foundations}
\resumeItem{AWS ML for Natural Language Processing}

\resumeSubHeadingListEnd

\end{document}